---
title: "Final Project"
author: "Abdellah AitElmouden | Gabriel Abreu |  Jered Ataky"
date: "12/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Research Objectives

Nutritional factors play a key role in both innate and adaptive immunity.4 Further, we have learnt that individuals with comorbidities are disproportionally affected with severe COVID-19 disease and mortality. Obesity, type 2 diabetes, atherosclerotic cardiovascular disease, and hypertension are risk factors for severe COVID-19.5 6 The aetiology of these conditions is largely driven by poor nutrition and unfavourable lifestyle choices (eg, physical inactivity or sedentary behaviour) 

The goal of this analysis is to find out how a country’s diet correlates with its COVID-19 mortality rate. With different food cultures across the world, it would be interesting to see what are the food categories that can best predict a country’s rate of deaths.

## The Dataset

Data for this project is taken from this very interesting [kaggle](https://www.kaggle.com/mariaren/covid19-healthy-diet-dataset) dataset. the dataset combined data of different types of food, world population obesity and undernourished rate, and global COVID-19 cases count from around the world in order to learn more about how a healthy eating style could help combat the Corona Virus.

There are 5 files in the dataset:

- Fat_Supply_Quantity_Data.csv: percentage of fat intake from different food groups for 170 different countries.
- Food_Supply_Quantity_kg_Data.csv: percentage of food intake( in  kg  ) from different food groups for 170 different countries.
- Food_Supply_kcal_Data.csv: percentage of energy intake (in  kcal ) from different food groups for 170 different countries.
- Protein_Supply_Quantity_Data.csv: percentage of protein intake from different food groups for 170 different countries.
All of these files have, also, columns including obesity, undernourishment and COVID-19 cases as percentages of total population.
- Supply_Food_Data_Descriptions.csv: This dataset is obtained from FAO.org, and is used to show the specific types of food that belongs to each category for the above datasets.

```{r setup, include=FALSE}
# Import libraries
library(GGally)
library(ggplot2)
library(caret)
library(mice)
library(tidyverse)
library(DataExplorer)
library(MASS)
library(naniar)
```


## Data Exploration

```{r}
fat_data <- read.csv("./data/Fat_Supply_Quantity_Data.csv")
supply_kcal_data <- read.csv("./data/Food_Supply_kcal_Data.csv")
supply_kg_data <- read.csv("./data/Food_Supply_Quantity_kg_Data.csv")
protein_data <- read.csv("./data/Protein_Supply_Quantity_Data.csv")
```

In almost all dataset, the data are organized by countries. There are 170 countries in these datasets. 32 variables as following:

```{r}
names(supply_kcal_data)
```
By checking the datasets we notice that the datasets similar, and chose to focus on the easiest to understand: food_kg. Also the Unit column only contains the % sign, indicating that all the column except the Population one are in percentages. It is important to know the unit used.

## Check missing Data

```{r}
plot_missing(supply_kg_data,  missing_only = TRUE)
```
The plot helps us understanding that almost almost 4% of data are missing in the "Recovered", "Deaths", "Confirmed", ""Undernourished" and "Active" Variables. and almost 2% in the "Obesity".
